---
title: "Explore google health trends - 'corona'"
output:
  pdf_document: default
  html_document: default
  word_document: default
---

One sentence summary about objective of this doc -- to explore how the google search trend outcome var changes for terms we expect to change dramatically over the course of the pandemic.

Description of the outcome variable that google health trends returns -- A. 'Corona'. 

```{r load-libraries, warning=F, message=F, echo=F}
# install.packages("geofacet") #install once if you don't already have the package
library(geofacet) 
library(tidyverse)
library(magrittr)
library(gridExtra)
```

```{r import-data, echo=F, message=F}
#read in data
state_list <- c(paste0("US-", state.abb), "US-DC", "US")

for(i in state_list[1:52]){
  counter <- 1
  assign(i, read_csv(paste0("/Users/krisztafarkas/Box Sync/Google-search-data/COVID and Unemployment sample searches/corona/", i, "/", i, "-corona.csv")
  )
)
}
```

```{r tidy-the-data, echo=F}
#arrange data by date and add on state variable
WY_tidy <- `US-WY` %>% arrange(timestamp) %>% mutate(state = "WY")
WV_tidy <- `US-WV` %>% arrange(timestamp) %>% mutate(state = "WV")
WI_tidy <- `US-WI` %>% arrange(timestamp) %>% mutate(state = "WI")
WA_tidy <- `US-WA` %>% arrange(timestamp) %>% mutate(state = "WA")

VT_tidy <- `US-VT` %>% arrange(timestamp) %>% mutate(state = "VT")
VA_tidy <- `US-VA` %>% arrange(timestamp) %>% mutate(state = "VA")

UT_tidy <- `US-UT` %>% arrange(timestamp) %>% mutate(state = "UT")

TX_tidy <- `US-TX` %>% arrange(timestamp) %>% mutate(state = "TX")
TN_tidy <- `US-TN` %>% arrange(timestamp) %>% mutate(state = "TN")

SD_tidy <- `US-SD` %>% arrange(timestamp) %>% mutate(state = "SD")
SC_tidy <- `US-SC` %>% arrange(timestamp) %>% mutate(state = "SC")

RI_tidy <- `US-RI` %>% arrange(timestamp) %>% mutate(state = "RI")

PA_tidy <- `US-PA` %>% arrange(timestamp) %>% mutate(state = "PA")

OR_tidy <- `US-OR` %>% arrange(timestamp) %>% mutate(state = "OR")
OK_tidy <- `US-OK` %>% arrange(timestamp) %>% mutate(state = "OK")
OH_tidy <- `US-OH` %>% arrange(timestamp) %>% mutate(state = "OH")

NY_tidy <- `US-NY` %>% arrange(timestamp) %>% mutate(state = "NY")
NV_tidy <- `US-NV` %>% arrange(timestamp) %>% mutate(state = "NV")
NM_tidy <- `US-NM` %>% arrange(timestamp) %>% mutate(state = "NM")
NJ_tidy <- `US-NJ` %>% arrange(timestamp) %>% mutate(state = "NJ")
NH_tidy <- `US-NH` %>% arrange(timestamp) %>% mutate(state = "NH")
NE_tidy <- `US-NE` %>% arrange(timestamp) %>% mutate(state = "NE")
ND_tidy <- `US-ND` %>% arrange(timestamp) %>% mutate(state = "ND")
NC_tidy <- `US-NC` %>% arrange(timestamp) %>% mutate(state = "NC")

MT_tidy <- `US-MT` %>% arrange(timestamp) %>% mutate(state = "MT")
MS_tidy <- `US-MS` %>% arrange(timestamp) %>% mutate(state = "MS")
MO_tidy <- `US-MO` %>% arrange(timestamp) %>% mutate(state = "MO")
MN_tidy <- `US-MN` %>% arrange(timestamp) %>% mutate(state = "MN")
MI_tidy <- `US-MI` %>% arrange(timestamp) %>% mutate(state = "MI")
ME_tidy <- `US-ME` %>% arrange(timestamp) %>% mutate(state = "ME")
MD_tidy <- `US-MD` %>% arrange(timestamp) %>% mutate(state = "MD")
MA_tidy <- `US-MA` %>% arrange(timestamp) %>% mutate(state = "MA")

LA_tidy <- `US-LA` %>% arrange(timestamp) %>% mutate(state = "LA")

KY_tidy <- `US-KY` %>% arrange(timestamp) %>% mutate(state = "KY")
KS_tidy <- `US-KS` %>% arrange(timestamp) %>% mutate(state = "KS")

IN_tidy <- `US-IN` %>% arrange(timestamp) %>% mutate(state = "IN")
IL_tidy <- `US-IL` %>% arrange(timestamp) %>% mutate(state = "IL")
ID_tidy <- `US-ID` %>% arrange(timestamp) %>% mutate(state = "ID")
IA_tidy <- `US-IA` %>% arrange(timestamp) %>% mutate(state = "IA")

HI_tidy <- `US-HI` %>% arrange(timestamp) %>% mutate(state = "HI")

GA_tidy <- `US-GA` %>% arrange(timestamp) %>% mutate(state = "GA")

FL_tidy <- `US-FL` %>% arrange(timestamp) %>% mutate(state = "FL")

DE_tidy <- `US-DE` %>% arrange(timestamp) %>% mutate(state = "DE")
DC_tidy <- `US.DC` %>% arrange(timestamp) %>% mutate(state = "DC")

CT_tidy <- `US-CT` %>% arrange(timestamp) %>% mutate(state = "CT")
CO_tidy <- `US-CO` %>% arrange(timestamp) %>% mutate(state = "CO")
CA_tidy <- `US-CA` %>% arrange(timestamp) %>% mutate(state = "CA")

AZ_tidy <- `US-AZ` %>% arrange(timestamp) %>% mutate(state = "AZ")
AR_tidy <- `US-AR` %>% arrange(timestamp) %>% mutate(state = "AR")
AL_tidy <- `US-AL` %>% arrange(timestamp) %>% mutate(state = "AL")
AK_tidy <- `US-AK` %>% arrange(timestamp) %>% mutate(state = "AK")
US_tidy <- US %>% arrange(timestamp) %>% mutate(state = "Total US")

#stack into one data frame - deleted DC_tidy from between CT and DE for now
all <- bind_rows(US_tidy, AK_tidy, AL_tidy, AR_tidy, AZ_tidy, CA_tidy, CO_tidy, CT_tidy, DC_tidy, DE_tidy,
                 FL_tidy, GA_tidy, HI_tidy, IA_tidy, ID_tidy, IL_tidy, IN_tidy, KS_tidy, KY_tidy, LA_tidy,
                 MA_tidy, MD_tidy, ME_tidy, MI_tidy, MN_tidy, MO_tidy, MS_tidy, MT_tidy, NC_tidy, ND_tidy,
                 NE_tidy, NH_tidy, NJ_tidy, NM_tidy, NV_tidy, NY_tidy, OH_tidy, OK_tidy, OR_tidy, PA_tidy,
                 RI_tidy, SC_tidy, SD_tidy, TN_tidy, TX_tidy, UT_tidy, VA_tidy, VT_tidy, WA_tidy, WI_tidy,
                 WV_tidy, WY_tidy)

#all states, exclude total US
bystate <- bind_rows(AK_tidy, AL_tidy, AR_tidy, AZ_tidy, CA_tidy, CO_tidy, CT_tidy, DC_tidy, DE_tidy,
                 FL_tidy, GA_tidy, HI_tidy, IA_tidy, ID_tidy, IL_tidy, IN_tidy, KS_tidy, KY_tidy, LA_tidy,
                 MA_tidy, MD_tidy, ME_tidy, MI_tidy, MN_tidy, MO_tidy, MS_tidy, MT_tidy, NC_tidy, ND_tidy,
                 NE_tidy, NH_tidy, NJ_tidy, NM_tidy, NV_tidy, NY_tidy, OH_tidy, OK_tidy, OR_tidy, PA_tidy,
                 RI_tidy, SC_tidy, SD_tidy, TN_tidy, TX_tidy, UT_tidy, VA_tidy, VT_tidy, WA_tidy, WI_tidy,
                 WV_tidy, WY_tidy)

#by US region to better see varition in trends by state
# northeast: Connecticut, Maine, Massachusetts, New Hampshire, Rhode Island, Vermont, New Jersey, New York, Pennsylvania
northeast <- bind_rows(CT_tidy, ME_tidy, MA_tidy, NH_tidy, RI_tidy, VT_tidy, NJ_tidy, NY_tidy, PA_tidy)

# midwest: Illinois, Indiana, Michigan, Ohio, Wisconsin, Iowa, Kansas, Minnesota, Missouri, Nebraska, North Dekota, South Dekota
mdwest <- bind_rows(IL_tidy, IN_tidy, MI_tidy, OH_tidy, WI_tidy, IA_tidy, KS_tidy, MN_tidy, MO_tidy, NE_tidy, ND_tidy, SD_tidy)

# south: Delaware, Florida, Georgia, Maryland, North Carolina, South Carolina, Virginia, DC, West Virginia, Alabama, Kentucky, Mississippi, Tennessee, Arkansas, Louisiana, Oklahoma, Texas
south <- bind_rows(DE_tidy, FL_tidy, GA_tidy, MD_tidy, NC_tidy, SC_tidy, VA_tidy, DC_tidy, WV_tidy, AL_tidy, KY_tidy, MS_tidy, TN_tidy, AR_tidy, LA_tidy, OK_tidy, TX_tidy)

# west: Arizona, Colorado, Idaho, Montana, Nevada, New Mexico, Utah, Wyoming, Alaska, California, Hawaii, Oregon, Washington
west <- bind_rows(AZ_tidy, CO_tidy, ID_tidy, MT_tidy, NV_tidy, NM_tidy, UT_tidy, WY_tidy, AK_tidy, CA_tidy, HI_tidy, OR_tidy, WA_tidy)

```

```{r make-plots, echo = F, fig.height = 8, fig.width = 12}

#create plots
#plot of all states and geofacet
ggplot(bystate, aes(x = timestamp, y = value)) + geom_line(aes(col = state)) +
  labs(x = "Date", y = "Search outcome - 'corona'") + 
  ggtitle("All States, with total US (black dashed line)") + 
  geom_line(data = all %>% filter(state == "Total US"), linetype = "longdash")

ggplot(bystate, aes(x = timestamp, y = value)) + 
  geom_line(aes(col = state)) +
  labs(x = "Date", y = "Search outcome - 'corona'") + 
  ggtitle("\n\n\nBy State, with total US (black dashed line)") +
  facet_geo(~ state) + 
  geom_line(data = all %>% filter(state == "Total US"), linetype = "dashed")

#plots by region
p1 <- ggplot(northeast, aes(x = timestamp, y = value)) + geom_line(aes(col = state)) + 
  ylim(0,250000) +
  labs(x = "Date", y = "Search outcome - 'corona'") + 
  ggtitle("\n\n\nNortheastern States, with total US (black dashed line)") +
  geom_line(data = all %>% filter(state == "Total US"), linetype = "longdash")

p2 <- ggplot(mdwest, aes(x = timestamp, y = value)) + geom_line(aes(col = state)) +
  ylim(0,250000) +
  labs(x = "Date", y = "Search outcome - 'corona'") + 
  ggtitle("\n\n\nMidwestern States, with total US (black dashed line)") +
  geom_line(data = all %>% filter(state == "Total US"), linetype = "longdash")

p3 <- ggplot(south, aes(x = timestamp, y = value)) + geom_line(aes(col = state)) + 
  ylim(0,250000) +
  labs(x = "Date", y = "Search outcome - 'corona'") + 
  ggtitle("\n\nSouthern States, with total US (black dashed line)") +
  geom_line(data = all %>% filter(state == "Total US"), linetype = "longdash")

p4 <- ggplot(west, aes(x = timestamp, y = value)) + geom_line(aes(col = state)) + 
  ylim(0,250000) +
  labs(x = "Date", y = "Search outcome - 'corona'") + 
  ggtitle("\n\nWestern States, with total US (black dashed line)") + 
  geom_line(data = all %>% filter(state == "Total US"), linetype = "longdash")

grid.arrange(p1, p2, p3, p4, nrow = 2)
```


What next test should we run? What questions do we have for the group or Krista?

Questions:

KF: I'm probably not understanding what "value" is actually being captured by Google Health Trends, but I'm confused about why the trend for Total US isn't higher than for individual states.

