---
title: "Explore Google Health Trends child abuse-related search term test runs"
output:
  html_document: default
  word_document: default
  pdf_document: default
---
One sentence summary about objective of this doc -- to explore google health trends for child abuse-related search terms by examining data for 2019 (prior to study period).

Weekly searches in 2019 at the national and state levels for "hurt":

Terms included: hurt

Perpetrators included: mom, mother, stepmom, stepmother, mom's boyfriend, mom boyfriend, mom's girlfriend, mom girlfriend, mom's friend, mom friend, dad, father, stepdad, stepfather, dad's girlfriend, dad girlfriend, dad's friend, dad friend, dad's boyfriend, dad boyfriend, grandma, grandpa, brother, sister, uncle, aunt 


```{r load-libraries, warning=F, message=F, echo=F}
# install.packages("geofacet") #install once if you don't already have the package
library(directlabels)
library(geofacet) 
library(tidyverse)
library(magrittr)
library(gridExtra)
```

```{r import-data, echo=F, message=F}

## read in data
state_list <- c(paste0("US-", state.abb), "US-DC")

# "hit"
# read in US separately
US <- read_csv("/Users/krisztafarkas/Box Sync/Google-search-data/2019ExploratoryData/Child Abuse/Child-hurt-1/states/US/US-child-hurt-1.csv")

for(i in state_list[1:51]){
  counter <- 1
  assign(i, read_csv(paste0("/Users/krisztafarkas/Box Sync/Google-search-data/2019ExploratoryData/Child Abuse/Child-hurt-1/states/", i, "/", i, "-hurt-1.csv")
  )
)
}

```

```{r tidy-the-data, echo=F}
## clean/prep the data for plotting
## sort by date/time and add on additional variables as needed
WY_tidy <- `US-WY` %>% arrange(timestamp) %>% mutate(state = "WY")
WV_tidy <- `US-WV` %>% arrange(timestamp) %>% mutate(state = "WV")
WI_tidy <- `US-WI` %>% arrange(timestamp) %>% mutate(state = "WI")
WA_tidy <- `US-WA` %>% arrange(timestamp) %>% mutate(state = "WA")

VT_tidy <- `US-VT` %>% arrange(timestamp) %>% mutate(state = "VT")
VA_tidy <- `US-VA` %>% arrange(timestamp) %>% mutate(state = "VA")

UT_tidy <- `US-UT` %>% arrange(timestamp) %>% mutate(state = "UT")

TX_tidy <- `US-TX` %>% arrange(timestamp) %>% mutate(state = "TX")
TN_tidy <- `US-TN` %>% arrange(timestamp) %>% mutate(state = "TN")

SD_tidy <- `US-SD` %>% arrange(timestamp) %>% mutate(state = "SD")
SC_tidy <- `US-SC` %>% arrange(timestamp) %>% mutate(state = "SC")

RI_tidy <- `US-RI` %>% arrange(timestamp) %>% mutate(state = "RI")

PA_tidy <- `US-PA` %>% arrange(timestamp) %>% mutate(state = "PA")

OR_tidy <- `US-OR` %>% arrange(timestamp) %>% mutate(state = "OR")
OK_tidy <- `US-OK` %>% arrange(timestamp) %>% mutate(state = "OK")
OH_tidy <- `US-OH` %>% arrange(timestamp) %>% mutate(state = "OH")

NY_tidy <- `US-NY` %>% arrange(timestamp) %>% mutate(state = "NY")
NV_tidy <- `US-NV` %>% arrange(timestamp) %>% mutate(state = "NV")
NM_tidy <- `US-NM` %>% arrange(timestamp) %>% mutate(state = "NM")
NJ_tidy <- `US-NJ` %>% arrange(timestamp) %>% mutate(state = "NJ")
NH_tidy <- `US-NH` %>% arrange(timestamp) %>% mutate(state = "NH")
NE_tidy <- `US-NE` %>% arrange(timestamp) %>% mutate(state = "NE")
ND_tidy <- `US-ND` %>% arrange(timestamp) %>% mutate(state = "ND")
NC_tidy <- `US-NC` %>% arrange(timestamp) %>% mutate(state = "NC")

MT_tidy <- `US-MT` %>% arrange(timestamp) %>% mutate(state = "MT")
MS_tidy <- `US-MS` %>% arrange(timestamp) %>% mutate(state = "MS")
MO_tidy <- `US-MO` %>% arrange(timestamp) %>% mutate(state = "MO")
MN_tidy <- `US-MN` %>% arrange(timestamp) %>% mutate(state = "MN")
MI_tidy <- `US-MI` %>% arrange(timestamp) %>% mutate(state = "MI")
ME_tidy <- `US-ME` %>% arrange(timestamp) %>% mutate(state = "ME")
MD_tidy <- `US-MD` %>% arrange(timestamp) %>% mutate(state = "MD")
MA_tidy <- `US-MA` %>% arrange(timestamp) %>% mutate(state = "MA")

LA_tidy <- `US-LA` %>% arrange(timestamp) %>% mutate(state = "LA")

KY_tidy <- `US-KY` %>% arrange(timestamp) %>% mutate(state = "KY")
KS_tidy <- `US-KS` %>% arrange(timestamp) %>% mutate(state = "KS")

IN_tidy <- `US-IN` %>% arrange(timestamp) %>% mutate(state = "IN")
IL_tidy <- `US-IL` %>% arrange(timestamp) %>% mutate(state = "IL")
ID_tidy <- `US-ID` %>% arrange(timestamp) %>% mutate(state = "ID")
IA_tidy <- `US-IA` %>% arrange(timestamp) %>% mutate(state = "IA")

HI_tidy <- `US-HI` %>% arrange(timestamp) %>% mutate(state = "HI")

GA_tidy <- `US-GA` %>% arrange(timestamp) %>% mutate(state = "GA")

FL_tidy <- `US-FL` %>% arrange(timestamp) %>% mutate(state = "FL")

DE_tidy <- `US-DE` %>% arrange(timestamp) %>% mutate(state = "DE")
DC_tidy <- `US-DC` %>% arrange(timestamp) %>% mutate(state = "DC")

CT_tidy <- `US-CT` %>% arrange(timestamp) %>% mutate(state = "CT")
CO_tidy <- `US-CO` %>% arrange(timestamp) %>% mutate(state = "CO")
CA_tidy <- `US-CA` %>% arrange(timestamp) %>% mutate(state = "CA")

AZ_tidy <- `US-AZ` %>% arrange(timestamp) %>% mutate(state = "AZ")
AR_tidy <- `US-AR` %>% arrange(timestamp) %>% mutate(state = "AR")
AL_tidy <- `US-AL` %>% arrange(timestamp) %>% mutate(state = "AL")
AK_tidy <- `US-AK` %>% arrange(timestamp) %>% mutate(state = "AK")
US_tidy <- US %>% arrange(timestamp) %>% mutate(state = "Total US")

#stack into one data frame 
all <- bind_rows(US_tidy, AK_tidy, AL_tidy, AR_tidy, AZ_tidy, CA_tidy, CO_tidy, CT_tidy, DC_tidy, DE_tidy,
                 FL_tidy, GA_tidy, HI_tidy, IA_tidy, ID_tidy, IL_tidy, IN_tidy, KS_tidy, KY_tidy, LA_tidy,
                 MA_tidy, MD_tidy, ME_tidy, MI_tidy, MN_tidy, MO_tidy, MS_tidy, MT_tidy, NC_tidy, ND_tidy,
                 NE_tidy, NH_tidy, NJ_tidy, NM_tidy, NV_tidy, NY_tidy, OH_tidy, OK_tidy, OR_tidy, PA_tidy,
                 RI_tidy, SC_tidy, SD_tidy, TN_tidy, TX_tidy, UT_tidy, VA_tidy, VT_tidy, WA_tidy, WI_tidy,
                 WV_tidy, WY_tidy)

bystate <- bind_rows(AK_tidy, AL_tidy, AR_tidy, AZ_tidy, CA_tidy, CO_tidy, CT_tidy, DC_tidy, DE_tidy,
                 FL_tidy, GA_tidy, HI_tidy, IA_tidy, ID_tidy, IL_tidy, IN_tidy, KS_tidy, KY_tidy, LA_tidy,
                 MA_tidy, MD_tidy, ME_tidy, MI_tidy, MN_tidy, MO_tidy, MS_tidy, MT_tidy, NC_tidy, ND_tidy,
                 NE_tidy, NH_tidy, NJ_tidy, NM_tidy, NV_tidy, NY_tidy, OH_tidy, OK_tidy, OR_tidy, PA_tidy,
                 RI_tidy, SC_tidy, SD_tidy, TN_tidy, TX_tidy, UT_tidy, VA_tidy, VT_tidy, WA_tidy, WI_tidy,
                 WV_tidy, WY_tidy)

#by US region to better see varition in trends by state
# northeast: Connecticut, Maine, Massachusetts, New Hampshire, Rhode Island, Vermont, New Jersey, New York, Pennsylvania
northeast <- bind_rows(CT_tidy, ME_tidy, MA_tidy, NH_tidy, RI_tidy, VT_tidy, NJ_tidy, NY_tidy, PA_tidy)

# midwest: Illinois, Indiana, Michigan, Ohio, Wisconsin, Iowa, Kansas, Minnesota, Missouri, Nebraska, North Dekota, South Dekota
mdwest <- bind_rows(IL_tidy, IN_tidy, MI_tidy, OH_tidy, WI_tidy, IA_tidy, KS_tidy, MN_tidy, MO_tidy, NE_tidy, ND_tidy, SD_tidy)

# south: Delaware, Florida, Georgia, Maryland, North Carolina, South Carolina, Virginia, DC, West Virginia, Alabama, Kentucky, Mississippi, Tennessee, Arkansas, Louisiana, Oklahoma, Texas
south <- bind_rows(DE_tidy, FL_tidy, GA_tidy, MD_tidy, NC_tidy, SC_tidy, VA_tidy, DC_tidy, WV_tidy, AL_tidy, KY_tidy, MS_tidy, TN_tidy, AR_tidy, LA_tidy, OK_tidy, TX_tidy)

# west: Arizona, Colorado, Idaho, Montana, Nevada, New Mexico, Utah, Wyoming, Alaska, California, Hawaii, Oregon, Washington
west <- bind_rows(AZ_tidy, CO_tidy, ID_tidy, MT_tidy, NV_tidy, NM_tidy, UT_tidy, WY_tidy, AK_tidy, CA_tidy, HI_tidy, OR_tidy, WA_tidy)
```

```{r make-plots, echo = F, fig.height = 8, fig.width = 12}
## Create plots
## plot of all states and geofacet
ggplot(bystate, aes(x = timestamp, y = value)) + geom_line(aes(col = state)) +
  labs(x = "Date", y = "Search outcome - 'hurt'") + 
  ggtitle("\n\n\nSearch Term 'Hurt' - All States, with total US (black line)") + 
  geom_line(data = all %>% filter(state == "Total US"), linetype = "solid")

ggplot(bystate, aes(x = timestamp, y = value)) + 
  geom_line(aes(col = state)) +
  labs(x = "Date", y = "Search outcome - 'hurt'") + 
  theme(axis.text.x=element_blank(), axis.ticks.x=element_blank()) +
  ggtitle("\n\n\nSearch Term 'Hurt' - By State, with total US (black line)") +
  facet_geo(~ state) + 
  geom_line(data = all %>% filter(state == "Total US"), linetype = "solid")

#plots by region
p1a <- ggplot(northeast, aes(x = timestamp, y = value)) + geom_line(aes(col = state)) + 
  ylim(0,80) +
  labs(x = "Date", y = "Search outcome - 'hurt'") + 
  ggtitle("\n\n\n\'Hurt' - Northeastern States, with total US (black line)") +
  geom_line(data = all %>% filter(state == "Total US"), linetype = "longdash") +
  geom_dl(aes(label = state), method = list(dl.combine("first.points", "last.points"), cex = 0.8)) 

p2a <- ggplot(mdwest, aes(x = timestamp, y = value)) + geom_line(aes(col = state)) +
  ylim(0,80) +
  labs(x = "Date", y = "Search outcome - 'hurt'") + 
  ggtitle("\n\n\n'Hurt' - Midwestern States, with total US (black line)") +
  geom_line(data = all %>% filter(state == "Total US"), linetype = "longdash") +
  geom_dl(aes(label = state), method = list(dl.combine("first.points", "last.points"), cex = 0.8)) 

p3a <- ggplot(south, aes(x = timestamp, y = value)) + geom_line(aes(col = state)) + 
  ylim(0,80) +
  labs(x = "Date", y = "Search outcome - 'hurt'") + 
  ggtitle("\n\n'Hurt' - Southern States, with total US (black line)") +
  geom_line(data = all %>% filter(state == "Total US"), linetype = "longdash") +
  geom_dl(aes(label = state), method = list(dl.combine("first.points", "last.points"), cex = 0.8)) 

p4a <- ggplot(west, aes(x = timestamp, y = value)) + geom_line(aes(col = state)) + 
  ylim(0,80) +
  labs(x = "Date", y = "Search outcome - 'hurt'") + 
  ggtitle("\n\n'Hurt' - Western States, with total US (black line)") + 
  geom_line(data = all %>% filter(state == "Total US"), linetype = "longdash") +
  geom_dl(aes(label = state), method = list(dl.combine("first.points", "last.points"), cex = 0.8)) 

grid.arrange(p1a, p2a, p3a, p4a, nrow = 2)

```

