---
title: "Explore Google Health Trends intimate partner violence-related search term test runs"
output:
  html_document: default
  word_document: default
  pdf_document: default
---
One sentence summary about objective of this doc -- to explore google health trends intimate partner violence-related search terms by examining data pulled for 2019 (prior to study period).

National weekly searches for 2019:

Perpetrators included: husband, boyfriend, ex-boyfriend, ex-husband, ex boyfriend, ex husband, exboyfriend, exhusband, wife, girlfriend, ex-wife, ex-girlfriend, ex wife, ex girlfriend, exwife, exgirlfriend, partner, ex-partner, expartner, ex partner, spouse, ex-spouse, exspouse, ex spouse, ex, significant other 


```{r load-libraries, warning=F, message=F, echo=F}
# install.packages("geofacet") #install once if you don't already have the package
library(geofacet) 
library(tidyverse)
library(magrittr)
library(gridExtra)
library(stringr)
```

```{r import-data, echo=F, message=F}

#read in and clean data

####################
## Physical abuse ##
####################
#term_list1 <- cbind('hit', 'hits', 'hurt', 'hurts', 'kick', 'kicks', 'kicked', 'beat', 'beats', 'slap', 'slaps', 'slapped', 'grab', 'grabs', 'grabbed', 'push', 'pushes', 'pushed', 'harm', 'harms', 'harmed', 'punch', 'punches', 'punched', 'choke', 'chokes', 'choked', 'strangle', 'strangles', 'strangled', 'slam', 'slams', 'slammed')

#Set filepath for highest level query folder
Myfilepath.phys <- "/Users/krisztafarkas/Box Sync/Google-search-data/2019ExploratoryData/May 28 - June 3 Exploratory Searches/IPV/"

#Find all files in the subfolders
filenames.phys1 <- list.files(Myfilepath.phys, full.names = TRUE, recursive = TRUE, ignore.case = TRUE)
#exclude IPV - Asking for help queries
filenames.phys <- filenames.phys1[11:145]

#Read in all files and add a new column with the filepath
#Then parse the filepath into individual columns for each subsubfolder
AllQueries.phys <- filenames.phys %>%
  setNames(nm = .) %>%
  map_df(~read_csv(.x, col_types = cols(), col_names = TRUE), .id = "file_name") %>%
  separate("file_name", c("Blank","Users","Name","Box","Project","Exploratory","DateRange","Abuse-Cat", "Extra","Query","StatesFolder","State","Filename"), "/")

#Create new dataframe with only the columns we're interested in and then group by query and arrange by time
DataToGraph.phys <- select(AllQueries.phys,-"Blank",-"Users",-"Name",-"Box",-"Project",-"Exploratory",-"DateRange", -"Extra",-"StatesFolder",-"Filename", -"query_time", -"sample") %>%
  group_by(Query) %>%
  arrange(timestamp, .by_group=TRUE)

# Restrict to only national weekly data ('hit' and 'hurt' have state-level data too)
DataToGraph.phys <- DataToGraph.phys[which(DataToGraph.phys$State=='US'),]

# Create a column with cleaner versions of the query terms for plotting
Query2 <- unlist(strsplit(DataToGraph.phys$Query, split='-1', fixed=TRUE))

DataToGraph.phys <- cbind(DataToGraph.phys, Query2=Query2)

#####################
## Emotional abuse ##
#####################

#term_list2 <- cbind("afraid-of", "makes-me-afraid", "control", "controlled", "controls", "controlling", "does-not-care", "doesnt-care", "doesn-t-care", "does-not-love", "doesnt-love", "doesn-t-love", "unsafe", "feel-unsafe", "makes-me-feel-unsafe", "hate", "hates", "hating", "insult", "insulted", "insults", "insulting", "put-down", "puts-down", "putting-down", "scare-me", "scared-me", "scares-me", "scaring-me", "scared-of", "swear", "swore", "swears", "swearing", "threaten", "threatened", "threatens", "threatening", "yell", "yelled", "yells", "yelling")

#Set filepath for highest level query folder
Myfilepath.emo <- "/Users/krisztafarkas/Box Sync/Google-search-data/2019ExploratoryData/June 4-11 Exploratory Searches/IPV Emotional Abuse/"

#Find all files in the subfolders
filenames.emo <- list.files(Myfilepath.emo, full.names = TRUE, recursive = TRUE, ignore.case = TRUE)

#Read in all files and add a new column with the filepath
#Then parse the filepath into individual columns for each subsubfolder
AllQueries.emo <- filenames.emo %>%
  setNames(nm = .) %>%
  map_df(~read_csv(.x, col_types = cols(), col_names = TRUE), .id = "file_name") %>%
  separate("file_name", c("Blank","Users","Name","Box","Project","Exploratory","DateRange","Abuse-Cat", "Extra","Query","StatesFolder","State","Filename"), "/")

#Create new dataframe with only the columns we're interested in and then group by query and arrange by time
DataToGraph.emo <- select(AllQueries.emo,-"Blank",-"Users",-"Name",-"Box",-"Project",-"Exploratory",-"DateRange", -"Extra",-"StatesFolder",-"Filename", -"query_time", -"sample") %>%
  group_by(Query) %>% 
  arrange(timestamp, .by_group=TRUE)

# Create a column with cleaner versions of the query terms for plotting
Query2 <- unlist(strsplit(DataToGraph.emo$Query, split='-1', fixed=TRUE))

DataToGraph.emo <- cbind(DataToGraph.emo, Query2=Query2)

##################
## Sexual abuse ##
##################

#Set filepath for highest level query folder
Myfilepath.sex <- "/Users/krisztafarkas/Box Sync/Google-search-data/2019ExploratoryData/June 4-11 Exploratory Searches/IPV Sexual Abuse/"

#Find all files in the subfolders
filenames.sex <- list.files(Myfilepath.sex, full.names = TRUE, recursive = TRUE, ignore.case = TRUE)

#Read in all files and add a new column with the filepath
#Then parse the filepath into individual columns for each subsubfolder
AllQueries.sex <- filenames.sex %>%
  setNames(nm = .) %>%
  map_df(~read_csv(.x, col_types = cols(), col_names = TRUE), .id = "file_name") %>%
  separate("file_name", c("Blank","Users","Name","Box","Project","Exploratory","DateRange","Abuse-Cat", "Extra","Query","StatesFolder","State","Filename"), "/")

#Create new dataframe with only the columns we're interested in and then group by query and arrange by time
DataToGraph.sex <- select(AllQueries.sex,-"Blank",-"Users",-"Name",-"Box",-"Project",-"Exploratory",-"DateRange", -"Extra",-"StatesFolder",-"Filename", -"query_time", -"sample") %>%
  group_by(Query) %>%
  arrange(timestamp, .by_group=TRUE)

```


```{r plot1, echo = F, fig.height = 10, fig.width = 14}
#plot physical abuse
#plot google health trends data individually for each term(s)
cat("IPV Physical Abuse")
ggplot(DataToGraph.phys, aes(x = timestamp, y = value)) +
  geom_line(color='darkblue') + 
  labs(x = "Date", y = "Search outcome") + 
  facet_wrap(~Query2, ncol=4, nrow=20)#, labeller=labeller(Query=Query2))

#plot by search term(s)
ggplot(DataToGraph.phys, aes(x = timestamp, y = value)) +
  geom_line(aes(col = Query2)) +
  labs(x = "Date", y = "Search outcome") + 
  ggtitle("\n\n\nNational weekly data for 2019, by IPV physical abuse search term") +
  labs(col="Search term") 

```

```{r plot2, echo = F, fig.height = 60, fig.width = 20}

#plot google health trends data individually for each term(s)
#Sexual abuse
cat("IPV Sexual Abuse")
ggplot(DataToGraph.sex, aes(x = timestamp, y = value)) +
  geom_line(color='darkblue') + 
  labs(x = "Date", y = "Search outcome") + 
  facet_wrap(~Query, ncol=4, nrow=60) +
  theme(axis.text = element_text(size = 10), 
        axis.title = element_text(size = 10, face = "bold"),
        strip.text = element_text(size = 10))
```

``` {r plot3, echo=F, fig.height = 10, fig.width = 14}
#plot emotional abuse
#plot google health trends data individually for each term(s)
cat("IPV Emotional Abuse")
ggplot(DataToGraph.emo, aes(x = timestamp, y = value)) +
  geom_line(color='darkblue') + 
  labs(x = "Date", y = "Search outcome") + 
  facet_wrap(~Query2, ncol=4, nrow=20)#, labeller=labeller(Query=Query2))

#plot by search term(s)
ggplot(DataToGraph.emo, aes(x = timestamp, y = value)) +
  geom_line(aes(col = Query2)) +
  labs(x = "Date", y = "Search outcome") + 
  ggtitle("\n\n\nNational weekly data for 2019, by IPV emotional abuse search term") +
  labs(col="Search term")
```
