---
title: "Explore Google Health Trends intimate partner violence-related search term test runs"
output:
  html_document: default
  word_document: default
  pdf_document: default
---
One sentence summary about objective of this doc -- to explore google health trends for intimate partner violence-related search terms by examining data for 2019 (prior to study period).

Weekly searches at the national level for 2019:

Terms include variations of: "how to text/what is/find abuse hotline number", "[perpetrator] abuses me", "how to develop code words to tell children to call 911", "I feel unsafe/husband/boyfriend/partner makes me feel unsafe", "abuse/domestic violence hotline/help/emergency line/helpline/support line", "women's/domestic violence shelter/ help for abused women", "how to keep partner/boyfriend/husband calm", "how to secretly save money", "how to leave abusive/dangerous relationship/marriage", "how to protect kinds from domestic violence"

Perpetrators included: husband, boyfriend, ex-boyfriend, ex-husband, ex boyfriend, ex husband, exboyfriend, exhusband, wife, girlfriend, ex-wife, ex-girlfriend, ex wife, ex girlfriend, exwife, exgirlfriend, partner, ex-partner, expartner, ex partner, spouse, ex-spouse, exspouse, ex spouse, ex, significant other


** Note the different y-axis scale for 'abuse/domestic violence hotline' searches in first set of plots.

```{r load-libraries, warning=F, message=F, echo=F}
#install.packages("geofacet") #install once if you don't already have the package
library(directlabels)
library(geofacet) 
library(tidyverse)
library(magrittr)
library(gridExtra)
```

```{r import-data, echo=F, message=F}

#read in data
#create term-specific dataframes
find.abuse.hotline <- read_csv("/Users/krisztafarkas/Box Sync/Google-search-data/2019ExploratoryData/May 28 - June 3 Exploratory Searches/IPV/AskingForHelpQueries/US-IPV-abuse-hotline.csv")

abuses.me <- read_csv("/Users/krisztafarkas/Box Sync/Google-search-data/2019ExploratoryData/May 28 - June 3 Exploratory Searches/IPV/AskingForHelpQueries/US-IPV-abuses-me.csv")

codeword <- read_csv("/Users/krisztafarkas/Box Sync/Google-search-data/2019ExploratoryData/May 28 - June 3 Exploratory Searches/IPV/AskingForHelpQueries/US-IPV-codewords.csv")

unsafe <- read_csv("/Users/krisztafarkas/Box Sync/Google-search-data/2019ExploratoryData/May 28 - June 3 Exploratory Searches/IPV/AskingForHelpQueries/US-IPV-feel-unsafe.csv")

hotline <- read_csv("/Users/krisztafarkas/Box Sync/Google-search-data/2019ExploratoryData/May 28 - June 3 Exploratory Searches/IPV/AskingForHelpQueries/US-IPV-find-hotline.csv")

shelter <- read_csv("/Users/krisztafarkas/Box Sync/Google-search-data/2019ExploratoryData/May 28 - June 3 Exploratory Searches/IPV/AskingForHelpQueries/US-IPV-find-shelter.csv")

partner.calm <- read_csv("/Users/krisztafarkas/Box Sync/Google-search-data/2019ExploratoryData/May 28 - June 3 Exploratory Searches/IPV/AskingForHelpQueries/US-IPV-how-to-calm.csv")

save.money <- read_csv("/Users/krisztafarkas/Box Sync/Google-search-data/2019ExploratoryData/May 28 - June 3 Exploratory Searches/IPV/AskingForHelpQueries/US-IPV-how-to-secretly-save.csv")

leave <- read_csv("/Users/krisztafarkas/Box Sync/Google-search-data/2019ExploratoryData/May 28 - June 3 Exploratory Searches/IPV/AskingForHelpQueries/US-IPV-leave-relationship.csv")

protect.kids <- read_csv("/Users/krisztafarkas/Box Sync/Google-search-data/2019ExploratoryData/May 28 - June 3 Exploratory Searches/IPV/AskingForHelpQueries/US-IPV-protect-kids.csv")

dailyhotline <- read_csv("/Users/krisztafarkas/Box Sync/Google-search-data/2019ExploratoryData/June 4-11 Exploratory Searches/Daily Abuse Hotline Searches at National Level/Abuse-Hotline/states/US/US-IPV-daily-abuse-hotline.csv")

```

```{r tidy-the-data, echo=F}
find_hotline_tidy <- `find.abuse.hotline` %>% arrange(timestamp) %>% mutate(term2 = "how to find/text/what is hotline") %>% mutate(term3 = "how to - hotline")
abuseme_tidy <- `abuses.me` %>% arrange(timestamp) %>% mutate(term2 = "[perpetrator] abuses me") %>% mutate(term3 = "abuse me")
codeword_tidy <- `codeword` %>% arrange(timestamp) %>% mutate(term2 = "how to develop code word") %>% mutate(term3 = "codeword")
unsafe_tidy <- `unsafe` %>% arrange(timestamp) %>% mutate(term2 = "makes me feel unsafe") %>% mutate(term3 = "unsafe")
hotline_tidy <- `hotline` %>% arrange(timestamp) %>% mutate(term2 = "abuse/domestic violence hotline") %>% mutate(term3 = "hotline")
shelter_tidy <- `shelter` %>% arrange(timestamp) %>% mutate(term2 = "women's/domestic violence shelter") %>% mutate(term3 = "shelter")
calm_tidy <- `partner.calm` %>% arrange(timestamp) %>% mutate(term2 = "how to keep partner calm") %>% mutate(term3 = "calm")
money_tidy <- `save.money` %>% arrange(timestamp) %>% mutate(term2 = "how to secretly save money") %>% mutate(term3 = "money")
leave_tidy <- `leave` %>% arrange(timestamp) %>% mutate(term2 = "how to leave abusive/dangerous relationship") %>% mutate(term3 = "relationship")
protect_kids_tidy <- `protect.kids` %>% arrange(timestamp) %>% mutate(term2 = "protect kids from domestic violence") %>% mutate(term3 = "protect")

#weekly hotline query
dailyhotline_tidy <- `dailyhotline` %>% arrange(timestamp) %>% mutate(term2 = "abuse/domestic violence hotline") %>% mutate(term3 = "hotline")
#dailyhotline_tidy$timestamp


# stack all weekly queries into one dataframe
all <- bind_rows(find_hotline_tidy, abuseme_tidy, codeword_tidy, unsafe_tidy, hotline_tidy, shelter_tidy, calm_tidy, money_tidy, leave_tidy, protect_kids_tidy)

# exclude hotline_tidy because on such different scale
all.2 <- bind_rows(find_hotline_tidy, abuseme_tidy, codeword_tidy, unsafe_tidy, shelter_tidy, calm_tidy, money_tidy, leave_tidy, protect_kids_tidy)

```

```{r make-plots, echo = F, fig.height = 10, fig.width = 14}

#plot google health trends data individually for each term(s)
p1 <- ggplot(find_hotline_tidy, aes(x = timestamp, y = value)) +
  geom_line() + ylim(0,14) +
  labs(x = "Date", y = "Search outcome") + 
  ggtitle("'how to find/text/what is hotline' searches") 

p2 <- ggplot(abuseme_tidy, aes(x = timestamp, y = value)) +
  geom_line() +  ylim(0,14) +
  labs(x = "Date", y = "Search outcome") + 
  ggtitle("'[perpetrator] abuses me' searches")

p3 <- ggplot(codeword_tidy, aes(x = timestamp, y = value)) +
  geom_line() + ylim(0,14) +
  labs(x = "Date", y = "Search outcome") + 
  ggtitle("'how to develop code word' searches")

p4 <- ggplot(unsafe_tidy, aes(x = timestamp, y = value)) +
  geom_line() + ylim(0,14) +
  labs(x = "Date", y = "Search outcome") + 
  ggtitle("'makes me feel unsafe' searches")

p5 <- ggplot(hotline_tidy, aes(x = timestamp, y = value)) +
  geom_line() +  #ylim(0,3) +
  labs(x = "Date", y = "Search outcome") + 
  ggtitle("'abuse/domestic violence hotline' searches")

p6 <- ggplot(shelter_tidy, aes(x = timestamp, y = value)) +
  geom_line() + ylim(0,14) +
  labs(x = "Date", y = "Search outcome") + 
  ggtitle("'women's/domestic violence shelter' searches")

p7 <- ggplot(calm_tidy, aes(x = timestamp, y = value)) +
  geom_line() + ylim(0,14) +
  labs(x = "Date", y = "Search outcome") + 
  ggtitle("'how to keep partner calm' searches")

p8 <- ggplot(money_tidy, aes(x = timestamp, y = value)) +
  geom_line() +  ylim(0,14) +
  labs(x = "Date", y = "Search outcome") + 
  ggtitle("'how to secretly save money' searches")

p9 <- ggplot(leave_tidy, aes(x = timestamp, y = value)) +
  geom_line() + ylim(0,14) +
  labs(x = "Date", y = "Search outcome") + 
  ggtitle("'how to leave abusive/dangerous relationship' searches")

p10 <- ggplot(protect_kids_tidy, aes(x = timestamp, y = value)) +
  geom_line() + ylim(0,14) +
  labs(x = "Date", y = "Search outcome") + 
  ggtitle("'how to protect kids from domestic violence' searches")

grid.arrange(p1, p2, p3, p4, p5, p6, p7, p8, p9, p10, nrow = 4)

#plot by search term(s)
ggplot(all, aes(x = timestamp, y = value)) +
  geom_line(aes(col = term2)) +
  labs(x = "Date", y = "Search outcome") + 
  ggtitle("\n\n\nNational weekly data for 2019, by IPV asking for help search term") +
  labs(col="Search term") +
  geom_dl(aes(label = term3), method = list(dl.combine("first.points"), cex = 0.8)) +
  coord_cartesian(clip = 'off')


ggplot(all.2, aes(x = timestamp, y = value)) +
  geom_line(aes(col = term2)) +
  labs(x = "Date", y = "Search outcome") + 
  ggtitle("\n\nNational weekly data for 2019, by IPV asking for help search term (excluding 'abuse/domestic violence hotline' searches)") +
  labs(col="Search term") +
  geom_dl(aes(label = term3), method = list(dl.combine("first.points"), cex = 0.8)) + 
  coord_cartesian(clip = 'off')

```

Daily searches at the national level for 2019 for "abuse/domestic violence hotline/help/emergency line/helpline/support line" - to examine for expected spikes on days when people drink more (e.g., New Years) as a data validity check

```{r make-plots2, echo = F, fig.height = 8, fig.width = 12}

#plot google health trends data individually for each term
ggplot(dailyhotline_tidy, aes(x = timestamp, y = value)) +
  geom_line() +
  labs(x = "Date", y = "Search outcome") + 
  scale_x_datetime(date_breaks = ("1 month")) +
  ggtitle("\n\nNational daily data for 2019 - 'abuse/domestic violence hotline' searches") 
