---
title: "Explore Google Health Trends baby-related search term test runs"
output:
  html_document: default
  word_document: default
  pdf_document: default
---
One sentence summary about objective of this doc -- to explore google health trends for baby-related search terms by examining data for 2019 (prior to study period).

Weekly searches at the national level for 2019:

Terms include variations of: "concussions in baby", "bruises in baby", "when to call 911 for [shaken baby/bruises in baby/concussion in baby/baby head injury]", "when to go to [ER/emergency room/ED/emergency department/hospital] for [shaken baby/bruises in baby/concussion in baby/baby head injury". Note: additional query with all the same terms except substituting "babies" instead of "baby"


```{r load-libraries, warning=F, message=F, echo=F}
# install.packages("geofacet") #install once if you don't already have the package
library(geofacet) 
library(tidyverse)
library(magrittr)
library(gridExtra)
```

```{r import-data, echo=F, message=F}

#read in data
#create term-specific dataframes
baby <- read_csv("/Users/krisztafarkas/Box Sync/Google-search-data/2019ExploratoryData/June 4-11 Exploratory Searches/Baby Searches/Baby/states/US/US-baby-searches.csv")

babies <- read_csv("/Users/krisztafarkas/Box Sync/Google-search-data/2019ExploratoryData/June 4-11 Exploratory Searches/Baby Searches/Babies/states/US/US-babies-searches.csv")

```

```{r tidy-the-data, echo=F}
baby_tidy <- `baby` %>% arrange(timestamp) %>% mutate(term2 = "baby harm search terms")
babies_tidy <- `babies` %>% arrange(timestamp) %>% mutate(term2 = "babies variation of harm search terms")

# stack into one dataframe
all <- bind_rows(baby_tidy, babies_tidy)

```

```{r make-plots, echo = F, fig.height = 8, fig.width = 12}

#plot by search term(s)
ggplot(all, aes(x = timestamp, y = value)) +
  geom_line(aes(col = term2)) +
  labs(x = "Date", y = "Search outcome") + 
  ggtitle("National weekly data for 2019, by baby harm-related search terms") +
  labs(col="Search term") 

```


