---
title: "Explore google health trends"
output: html_document
---

Add one sentence summary about objective of this doc -- to explore how the google search trend outcome var changes for terms we expect to change dramatically over the course of the pandemic.

Also add description of the outcome variable that google health trends returns. 

```{r load-libraries, warning=F, message=F, echo=F}
library(tidyverse)
library(magrittr)
```

```{r import-data, echo=F, message=F}
#update to your directory path
US <-read_csv("/Users/corinneriddell/Box Sync/Google-search-data/corona/US/US-corona.csv")

state_list <- paste0("US-", state.abb)

#create state data frames
for(i in state_list[1:50]){
  counter <- 1
  assign(i, read_csv(paste0("/Users/corinneriddell/Box Sync/Google-search-data/corona/",
                            i, "/", i, "-corona.csv")
  )
)
}
```

```{r tidy-the-data, echo=F}
#generalize the code below to run for other states
AK_tidy <- `US-AK` %>% arrange(timestamp) %>% mutate(state = "AK")
US_tidy <- US %>% arrange(timestamp) %>% mutate(state = "ALL")

#stack into one data frame
all <- bind_rows(US_tidy, AK_tidy)
```

```{r make-plots, echo = F}
#plot
ggplot(all, aes(x = timestamp, y = value)) + geom_line(aes(col = state)) +
  labs(x = "Date", y = "Search outcome") 
```

Add sections for the other terms: unemployment, "Covid or Coronavirus"

What next test should we run? What qus do we have for the group or krista?

