---
title: "Explore google health trends - 'unemployment'"
output: html_document
---
One sentence summary about objective of this doc -- to explore how the google search trend outcome var changes for terms we expect to change dramatically over the course of the pandemic.

Description of the outcome variable that google health trends returns -- C. 'Unemployment'. 

```{r load-libraries, warning=F, message=F, echo=F}
# install.packages("geofacet") #install once if you don't already have the package
library(geofacet) 
library(tidyverse)
library(magrittr)
library(gridExtra)
```

```{r import-data, echo=F, message=F}

#update to your directory path
#fixing formatting of "query_time" variable, otherwise get error
US <-read_csv("/Users/corinneriddell/Box Sync/Google-search-data/unemployment/US/US-unemployment.csv", 
              col_types = cols(query_time = col_character(), sample = col_double(), 
                               term = col_character(), timestamp = col_date(format = "%m/%d/%Y"), value = col_double()))

#create DC data frame separately - this was causing an error so had to work around it
US.DC <- read_csv("/Users/corinneriddell/Box Sync/Google-search-data/unemployment/US-DC/US-DC-unemployment.csv")
US.DC %<>% mutate(timestamp = as.Date(timestamp))

state_list <- paste0("US-", state.abb)

#create state data frames
for(i in state_list[1:50]){
  counter <- 1
  assign(i, read_csv(paste0("/Users/corinneriddell/Box Sync/Google-search-data/unemployment/",
                            i, "/", i, "-unemployment.csv")#, 
                            # col_types = cols(query_time = col_character(), 
                            #                  sample = col_double(), 
                            #                  term = col_character(), 
                            #                  timestamp = col_date(format = ""), 
                            #                  value = col_double()))
  )
)
}

try <- bind_rows(US %>% select(-query_time), 
                 US.DC %>% select(-query_time), 
                 `US-CA` %>% select(-query_time) %>% mutate(timestamp =  as.Date(timestamp))
)

```

```{r tidy-the-data, echo=F}
#generalize the code below to run for other states
#KF: getting Error: cannot arrange column of class 'function' at position 1"
WY_tidy <- `US-WY` %>% arrange(timestamp) %>% mutate(state = "WY")  %>% select(-query_time)

WV_tidy <- `US-WV` %>% arrange(timestamp) %>% mutate(state = "WV") %>% select(-query_time)

WI_tidy <- `US-WI` %>% arrange(timestamp) %>% mutate(state = "WI") %>% select(-query_time)

WA_tidy <- `US-WA` %>% arrange(timestamp) %>% mutate(state = "WA") %>% select(-query_time)



VT_tidy <- `US-VT` %>% arrange(timestamp) %>% mutate(state = "VT") %>% select(-query_time)

VA_tidy <- `US-VA` %>% arrange(timestamp) %>% mutate(state = "VA") %>% select(-query_time)



UT_tidy <- `US-UT` %>% arrange(timestamp) %>% mutate(state = "UT") %>% select(-query_time)



TX_tidy <- `US-TX` %>% arrange(timestamp) %>% mutate(state = "TX") %>% select(-query_time)

TN_tidy <- `US-TN` %>% arrange(timestamp) %>% mutate(state = "TN") %>% select(-query_time)



SD_tidy <- `US-SD` %>% arrange(timestamp) %>% mutate(state = "SD") %>% select(-query_time)

SC_tidy <- `US-SC` %>% arrange(timestamp) %>% mutate(state = "SC") %>% select(-query_time)



RI_tidy <- `US-RI` %>% arrange(timestamp) %>% mutate(state = "RI") %>% select(-query_time)



PA_tidy <- `US-PA` %>% arrange(timestamp) %>% mutate(state = "PA") %>% select(-query_time)



OR_tidy <- `US-OR` %>% arrange(timestamp) %>% mutate(state = "OR") %>% select(-query_time)

OK_tidy <- `US-OK` %>% arrange(timestamp) %>% mutate(state = "OK") %>% select(-query_time)

OH_tidy <- `US-OH` %>% arrange(timestamp) %>% mutate(state = "OH") %>% select(-query_time)



NY_tidy <- `US-NY` %>% arrange(timestamp) %>% mutate(state = "NY") %>% select(-query_time)

NV_tidy <- `US-NV` %>% arrange(timestamp) %>% mutate(state = "NV") %>% select(-query_time)

NM_tidy <- `US-NM` %>% arrange(timestamp) %>% mutate(state = "NM") %>% select(-query_time)

NJ_tidy <- `US-NJ` %>% arrange(timestamp) %>% mutate(state = "NJ") %>% select(-query_time)

NH_tidy <- `US-NH` %>% arrange(timestamp) %>% mutate(state = "NH") %>% select(-query_time)

NE_tidy <- `US-NE` %>% arrange(timestamp) %>% mutate(state = "NE") %>% select(-query_time)

ND_tidy <- `US-ND` %>% arrange(timestamp) %>% mutate(state = "ND") %>% select(-query_time)

NC_tidy <- `US-NC` %>% arrange(timestamp) %>% mutate(state = "NC") %>% select(-query_time)



MT_tidy <- `US-MT` %>% arrange(timestamp) %>% mutate(state = "MT") %>% select(-query_time)

MS_tidy <- `US-MS` %>% arrange(timestamp) %>% mutate(state = "MS") %>% select(-query_time)

MO_tidy <- `US-MO` %>% arrange(timestamp) %>% mutate(state = "MO") %>% select(-query_time)

MN_tidy <- `US-MN` %>% arrange(timestamp) %>% mutate(state = "MN") %>% select(-query_time)

MI_tidy <- `US-MI` %>% arrange(timestamp) %>% mutate(state = "MI") %>% select(-query_time)

ME_tidy <- `US-ME` %>% arrange(timestamp) %>% mutate(state = "ME") %>% select(-query_time)

MD_tidy <- `US-MD` %>% arrange(timestamp) %>% mutate(state = "MD") %>% select(-query_time)

MA_tidy <- `US-MA` %>% arrange(timestamp) %>% mutate(state = "MA") %>% select(-query_time)



LA_tidy <- `US-LA` %>% arrange(timestamp) %>% mutate(state = "LA") %>% select(-query_time)

 

KY_tidy <- `US-KY` %>% arrange(timestamp) %>% mutate(state = "KY") %>% select(-query_time)

KS_tidy <- `US-KS` %>% arrange(timestamp) %>% mutate(state = "KS") %>% select(-query_time)



IN_tidy <- `US-IN` %>% arrange(timestamp) %>% mutate(state = "IN") %>% select(-query_time)

IL_tidy <- `US-IL` %>% arrange(timestamp) %>% mutate(state = "IL") %>% select(-query_time)

ID_tidy <- `US-ID` %>% arrange(timestamp) %>% mutate(state = "ID") %>% select(-query_time)

IA_tidy <- `US-IA` %>% arrange(timestamp) %>% mutate(state = "IA") %>% select(-query_time)



HI_tidy <- `US-HI` %>% arrange(timestamp) %>% mutate(state = "HI") %>% select(-query_time)



GA_tidy <- `US-GA` %>% arrange(timestamp) %>% mutate(state = "GA") %>% select(-query_time)



FL_tidy <- `US-FL` %>% arrange(timestamp) %>% mutate(state = "FL") %>% select(-query_time)



DE_tidy <- `US-DE` %>% arrange(timestamp) %>% mutate(state = "DE") %>% select(-query_time)

DC_tidy <- `US.DC` %>% arrange(timestamp) %>% mutate(state = "DC") %>% select(-query_time)



CT_tidy <- `US-CT` %>% arrange(timestamp) %>% mutate(state = "CT") %>% select(-query_time)

CO_tidy <- `US-CO` %>% arrange(timestamp) %>% mutate(state = "CO") %>% select(-query_time)

CA_tidy <- `US-CA` %>% arrange(timestamp) %>% mutate(state = "CA") %>% select(-query_time)



AZ_tidy <- `US-AZ` %>% arrange(timestamp) %>% mutate(state = "AZ") %>% select(-query_time)

AR_tidy <- `US-AR` %>% arrange(timestamp) %>% mutate(state = "AR") %>% select(-query_time)

AL_tidy <- `US-AL` %>% arrange(timestamp) %>% mutate(state = "AL") %>% select(-query_time)

AK_tidy <- `US-AK` %>% arrange(timestamp) %>% mutate(state = "AK") %>% select(-query_time)

US_tidy <- US %>% arrange(timestamp) %>% mutate(state = "Total US") %>% select(-query_time)


#stack into one data frame - deleted DC_tidy from between CT and DE for now
all <- bind_rows(US_tidy, AK_tidy, AL_tidy, AR_tidy, AZ_tidy, CA_tidy, CO_tidy, CT_tidy, DC_tidy, DE_tidy,
                 FL_tidy, GA_tidy, HI_tidy, IA_tidy, ID_tidy, IL_tidy, IN_tidy, KS_tidy, KY_tidy, LA_tidy,
                 MA_tidy, MD_tidy, ME_tidy, MI_tidy, MN_tidy, MO_tidy, MS_tidy, MT_tidy, NC_tidy, ND_tidy,
                 NE_tidy, NH_tidy, NJ_tidy, NM_tidy, NV_tidy, NY_tidy, OH_tidy, OK_tidy, OR_tidy, PA_tidy,
                 RI_tidy, SC_tidy, SD_tidy, TN_tidy, TX_tidy, UT_tidy, VA_tidy, VT_tidy, WA_tidy, WI_tidy,
                 WV_tidy, WY_tidy)

bystate <- bind_rows(AK_tidy, AL_tidy, AR_tidy, AZ_tidy, CA_tidy, CO_tidy, CT_tidy, DC_tidy, DE_tidy,
                 FL_tidy, GA_tidy, HI_tidy, IA_tidy, ID_tidy, IL_tidy, IN_tidy, KS_tidy, KY_tidy, LA_tidy,
                 MA_tidy, MD_tidy, ME_tidy, MI_tidy, MN_tidy, MO_tidy, MS_tidy, MT_tidy, NC_tidy, ND_tidy,
                 NE_tidy, NH_tidy, NJ_tidy, NM_tidy, NV_tidy, NY_tidy, OH_tidy, OK_tidy, OR_tidy, PA_tidy,
                 RI_tidy, SC_tidy, SD_tidy, TN_tidy, TX_tidy, UT_tidy, VA_tidy, VT_tidy, WA_tidy, WI_tidy,
                 WV_tidy, WY_tidy)

#by US region to better see varition in trends by state
# northeast: Connecticut, Maine, Massachusetts, New Hampshire, Rhode Island, Vermont, New Jersey, New York, Pennsylvania
northeast <- bind_rows(CT_tidy, ME_tidy, MA_tidy, NH_tidy, RI_tidy, VT_tidy, NJ_tidy, NY_tidy, PA_tidy)

# midwest: Illinois, Indiana, Michigan, Ohio, Wisconsin, Iowa, Kansas, Minnesota, Missouri, Nebraska, North Dekota, South Dekota
mdwest <- bind_rows(IL_tidy, IN_tidy, MI_tidy, OH_tidy, WI_tidy, IA_tidy, KS_tidy, MN_tidy, MO_tidy, NE_tidy, ND_tidy, SD_tidy)

# south: Delaware, Florida, Georgia, Maryland, North Carolina, South Carolina, Virginia, DC, West Virginia, Alabama, Kentucky, Mississippi, Tennessee, Arkansas, Louisiana, Oklahoma, Texas
south <- bind_rows(DE_tidy, FL_tidy, GA_tidy, MD_tidy, NC_tidy, SC_tidy, VA_tidy, DC_tidy, WV_tidy, AL_tidy, KY_tidy, MS_tidy, TN_tidy, AR_tidy, LA_tidy, OK_tidy, TX_tidy)

# west: Arizona, Colorado, Idaho, Montana, Nevada, New Mexico, Utah, Wyoming, Alaska, California, Hawaii, Oregon, Washington
west <- bind_rows(AZ_tidy, CO_tidy, ID_tidy, MT_tidy, NV_tidy, NM_tidy, UT_tidy, WY_tidy, AK_tidy, CA_tidy, HI_tidy, OR_tidy, WA_tidy)

```

```{r make-plots, echo = F, fig.height = 8, fig.width = 12}

#plot of all states and geofacet
ggplot(bystate, aes(x = timestamp, y = value)) + geom_line(aes(col = state)) +
  labs(x = "Date", y = "Search outcome - 'unemployment'") + 
  ggtitle("All States, with total US (black dashed line)") + 
  geom_line(data = all %>% filter(state == "Total US"), linetype = "longdash")

ggplot(bystate, aes(x = timestamp, y = value)) + 
  geom_line(aes(col = state)) +
  labs(x = "Date", y = "Search outcome - 'unemployment'") + 
  ggtitle("\n\n\nBy State, with total US (black dashed line)") +
  facet_geo(~ state) + 
  geom_line(data = all %>% filter(state == "Total US"), linetype = "dashed")

#plots by region
p1 <- ggplot(northeast, aes(x = timestamp, y = value)) + geom_line(aes(col = state)) + 
  #ylim(0,250000) +
  labs(x = "Date", y = "Search outcome - 'unemployment'") + 
  ggtitle("\n\n\nNortheastern States, with total US (black dashed line)") +
  geom_line(data = all %>% filter(state == "Total US"), linetype = "longdash")

p2 <- ggplot(mdwest, aes(x = timestamp, y = value)) + geom_line(aes(col = state)) +
  #ylim(0,250000) +
  labs(x = "Date", y = "Search outcome - 'unemployment'") + 
  ggtitle("\n\n\nMidwestern States, with total US (black dashed line)") +
  geom_line(data = all %>% filter(state == "Total US"), linetype = "longdash")

p3 <- ggplot(south, aes(x = timestamp, y = value)) + geom_line(aes(col = state)) + 
  #ylim(0,250000) +
  labs(x = "Date", y = "Search outcome - 'unemployment'") + 
  ggtitle("\n\nSouthern States, with total US (black dashed line)") +
  geom_line(data = all %>% filter(state == "Total US"), linetype = "longdash")

p4 <- ggplot(west, aes(x = timestamp, y = value)) + geom_line(aes(col = state)) + 
  #ylim(0,250000) +
  labs(x = "Date", y = "Search outcome - 'unemployment'") + 
  ggtitle("\n\nWestern States, with total US (black dashed line)") + 
  geom_line(data = all %>% filter(state == "Total US"), linetype = "longdash")

grid.arrange(p1, p2, p3, p4, nrow = 2)
```


What next test should we run? What questions do we have for the group or Krista?

Questions:

KF: I'm probably not understanding what "value" is actually being captured by Google Health Trends, but I'm confused about why the trend for Total US isn't higher than for individual states.
